\documentclass[a4paper,11pt]{article}

%A Few Useful Packages
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{latexsym}
\usepackage{marvosym}
\usepackage{fontspec} 					%for loading fonts
\usepackage{xunicode,xltxtra,url,parskip} 	%other packages for formatting
\RequirePackage{color,graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[big]{layaureo} 				%better formatting of the A4 page
% an alternative to Layaureo can be ** \usepackage{fullpage} **
\usepackage{supertabular} 				%for Grades
\usepackage{titlesec}					%custom \section
%Setup hyperref package, and colors for links
\usepackage{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}
\linespread{0.92}

%Page Setup
\usepackage{verbatim}
\usepackage{geometry}
\geometry{top=0.7in, bottom=0.7in, left=0.8in, right=0.8in}

%FONTS
\defaultfontfeatures{Mapping=tex-text}
%\setmainfont[SmallCapsFont = Fontin SmallCaps]{Fontin}
%%% modified for Karol Kozio? for ShareLaTeX use
\setmainfont[
SmallCapsFont = Fontin-SmallCaps.otf,
BoldFont = Fontin-Bold.otf,
ItalicFont = Fontin-Italic.otf
]
{Fontin.otf}
%%%

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{3pt}{3pt}
%Tweak a bit the top margin
%\addtolength{\voffset}{-1.3cm}

%-------------WATERMARK TEST [**not part of a CV**]---------------
\usepackage[absolute]{textpos}

\setlength{\TPHorizModule}{30mm}
\setlength{\TPVertModule}{\TPHorizModule}
\textblockorigin{2mm}{0.65\paperheight}
\setlength{\parindent}{0pt}

%--------------------BEGIN DOCUMENT----------------------
\begin{document}

\pagestyle{empty} % non-numbered pages

\font\fb=''[cmr10]'' %for use with \LaTeX command

%--------------------TITLE-------------
\par{\centering
		{\huge Shiyu \textsc{Dong}}
    \bigskip\par}

%--------------------SECTIONS-----------------------------------
%%%%%%%%%%%%% Section: Personal Information %%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-0.05 in} \section{Personal Information}
\begin{tabular}{rp{3.4cm}rl}
    \textsc{Cell Phone:} & +1 (512)927-7817 & \textsc{Address:} & 13630 Via Varra Apt 409, Broomfield, CO 80020\\
    \textsc{Work Phone:} & +1 (303)247-5116 & \textsc{email:}   & \href{mailto:shiyud@utexas.edu}{shiyud@utexas.edu}
\end{tabular}

%%%%%%%%%%%%% Section: Objective %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Objective}
Seeking for a full-time Software Development Engineer position starting immediately.

%%%%%%%%%%%%% Section: Work Experience %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Work Experience}

% Qualcomm Work
\textbf{Qualcomm Incorporated}, \emph{Software Engineer} \hfill \textsc{July 2014} - \emph{Present}\vspace{-10pt}\\
\begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=*]\vspace{-5pt}
\small{
  \item Work in Android Radio Interface Layer (RIL) team, which handles the communication between Android Telephony and Qualcomm modem.
  \item Responsible for RIL Network Access Service development tasks using C/C++.
  \item Lead Android Enhancement Multimedia Broadcast Multicast Service development tasks for RIL using C.
  \item Lead Android Access Terminal Command Forward (ATFwd) App and ATFwd Daemon development tasks using Java and C.
  \item Develop and maintain a RIL Unit Test Framework (UTF) in C++.
  \item Design and implement a Python based auto triage tool that can analyze and annotate RIL logs, decode hex messages in log and generate log summaries and call flow diagrams.
}
\end{itemize}

% RA
\begin{comment}
\textbf{The University of Texas at Austin}, \emph{Graduate Research Assistant} \hfill \textsc{Aug 2013 - Jan 2014}\vspace{-10pt}\\
\begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=*]\vspace{-5pt}
\small{
  \item Conducted research for the impact of different compiler optimizations on symbolic execution under the supervision of Dr. Sarfraz Khurshid.
}
\end{itemize}
\end{comment}

% Intern
\textbf{Qualcomm Incorporated}, \emph{Software Engineer Intern} \hfill\textsc{Jun 2013 - Aug 2013}\vspace{-10pt} \\
\begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=*]\vspace{-5pt}
\small{
  \item Refined UTF logging and implemented a log parser and HTML generator for UTF logs using Perl and Python.
  \item Optimized UTF framework to make it scalable to large number of test cases and able to take command line arguments.
  \item Designed a Python based auto test case generation tool that can convert RIL logs into executable UTF test cases.
}
\end{itemize}

% TA
\textbf{The University of Texas at Austin}, \emph{Teaching Assistant} \hfill\textsc{Jan 2013 - May 2014}\vspace{-10pt}\\
\begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=*]\vspace{-5pt}
\small{
  \item Teaching Assistant for \textit{Requirement Engineering} class taught by Dr. Suzanne Barber (2013) and Dr. Yinle Zhou (2014).
  \item Gained familiarity in the process of defining, documenting and maintaining software requirements, and different software development life cycle models including traditional waterfall model and agile model.
}
\end{itemize}

%%%%%%%%%%%%% Section: Education %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%&Software Engineering Track
\section{Education}
\textbf{The University of Texas at Austin} \hfill\textsc{Aug 2012 - May 2014}\vspace{-10pt}\\
\begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=*]\vspace{-5pt}
\small{
  \item \emph{M.S.E., Electrical and Computer Engineering} | \textsc{Gpa}: 3.82/4.0
  \item Thesis: "\href{http://repositories.lib.utexas.edu/bitstream/handle/2152/26000/DONG-THESIS-2014.pdf?sequence=1}{An Empirical Study of the Influence of Compiler Optimizations on Symbolic Execution}" supervised by Dr. Sarfraz Khurshid.
  \item Corresponding research paper "Studying the Influence of Standard Compiler Optimizations on Symbolic Execution" accepted and to appear on the 26th \emph{IEEE International Symposium on Software Reliability Engineering} (ISSRE) 2015.
}
\end{itemize}

%& University of Michigan - Shanghai Jiao Tong University Joint Institute \\
\textbf{Shanghai Jiao Tong University, Shanghai, China} \hfill\textsc{Sep 2008 - Aug 2012}\vspace{-10pt}\\
\begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=*]\vspace{-5pt}
\small{
  \item \emph{B.S., Electrical and Computer Engineering} | \textsc{Gpa}: 3.73/4.0
  \item Thesis: "Motor Control in Endoscopic Probes Based on Infrared Signals" supervised by Dr. Jigang Wu.
}
\end{itemize}

\begin{comment}
%%%%%%%%%%%%% Section: Research Experience %%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Research Experience}
\begin{tabular}{p{2.3cm}|p{14cm}}
  \hfill\textsc{Feb-May 2013} & Halide Compiler for Multicore Processor \\
  & \small Advisor: Dr. Keshav \textsc{Pingali}\\
  &\footnotesize{
  \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=*]\vspace{-5pt}
  \item Conduct research of Stencil Compiler and Halide programming language for image processing.
  \item Build a Halide compiler that can convert Halide language to C language
  using Python, with support of loop optimization, parallelization and vectorization.
  \item Evaluate the performance and analysis the difference between our implementation and the original Halide compiler.
\end{itemize} \vspace{-10pt}
}\\\multicolumn{2}{c}{} \vspace{-0.1 in} \\
 \hfill\textsc{Sep-Dec 2012} & Implementing Iterative Context Bounding in Java PathFinder (JPF) \\ 
 & \small Advisor: Dr. Sarfraz \textsc{Khurshid}\\
 &\footnotesize{
  \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=*]\vspace{-5pt}
   \item Study the basic usage JPF and understand iterative context bounding algorithm.
   \item Implement iterative context bounding in JPF 6.0. Resolve the state matching problem and perform depth bound optimization.
   \item Compare the performance with and without iterative context bounding algorithm against different benchmarks and analysis the result.
  \end{itemize} \vspace{-10pt}   
 }\\\multicolumn{2}{c}{} \vspace{-0.1 in} \\
\hfill\textsc{Sep-Dec 2011} & Motor Control in Endoscopic Probes Based on Infrared Signals \\
& \small Advisor: Dr. Jigang \textsc{Wu}\\
&\footnotesize{
\begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=*]\vspace{-5pt}
   \item Develop a motor control system for endoscope using infrared signal as medium.
   \item Design circuits based on a micro processor to process the signals and control the motor.
   \item Build a PHP web server. Establish the database. Use Java-Script and html to realize the web client page. Accomplish the control of the IR transmitting using the Wi-Fi based web server, and finally succeed in controlling the whole system.
  \end{itemize} \vspace{-10pt}
 }\\\multicolumn{2}{c}{} \vspace{-0.1 in} \\
 \hfill\textsc{Apr-Oct 2011} & Novel Integration Schemes for Multi-body Systems \\
& \small Advisor: Dr. Olivier \textsc{Bauchau}\\
&\footnotesize{
\begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=*]\vspace{-5pt}
   \item Study related concepts in multi-body dynamics and Lie Algebra.
   \item Study the Generalized-\begin{math}\alpha \end{math} method and classical method for solving 3D solid body motions.
   \item Develop software to perform convergence analysis of the energy-preserving integration scheme and appreciated the simplicity and high efficiency of this scheme.
   \item Publish paper {\it Intrinsic Time Integration Procedures for Rigid Body Dynamics} in {\it ASME Journal of Computational and Nonlinear Dynamics, 2011}.
  \end{itemize} \vspace{-10pt}
 }\\\multicolumn{2}{c}{} \vspace{-0.1 in} \\
\end{tabular}
\end{comment}

%Section: Knowledge and Skill Set
\section{Knowledge and Skill Set}
Solid foundation in data structures, algorithms, object oriented programming,
\textsc{Linux} environment programming, software testing, \textsc{Unix} system,
GNU tool chain and version control tools. Good understanding in operating
system, computer architecture, compiler (both front end and back end), software
engineering concept and requirement engineering concept.  Basic understanding
in computer networks.

%Section: Programming Languages
\section{Programming Languages}
\begin{tabular}{rl}
Fluent:& \textsc{c++}, \textsc{c}\\
Intermediate Knowledge:& \textsc{java}, \textsc{python}, \textsc{shell script}, \textsc{Matlab}, {\fb \LaTeX}\setmainfont[SmallCapsFont=Fontin-SmallCaps.otf]{Fontin.otf}\\
Basic Knowledge: & \textsc{perl}, \textsc{html}, \textsc{java-script},
\textsc{junit}, \textsc{VHDL}, \textsc{Alloy},
\textsc{Assembly}\\
\end{tabular}

\end{document}
